### 2013-03-28 doc/sosp13/tasks.tex
made up sample code

\Grappa provides four methods for expressing parallelism, shown in
Figure~\ref{fig:expressing-parallelism}. First, when the programmer identifies
work that can be done in parallel, the work may be wrapped up in a function
and queued with its arguments for later execution using a \texttt{spawn}.
Second, a programmer can use \texttt{spawn\_on} to spawn a task on a specific
core in the system or at the home core of a particular memory location. Third,
the programmer can invoke a parallel for loop, provided that the trip count is
known at loop entry. The programmer specifies a function pointer along with
start and end indices and an optional threshold to control parallel overhead.
\Grappa does {\em recursive decomposition} of iterations, similar to Cilk's
cilk\_for construct~\cite {cilkforimplementation}, and TBB's {\tt
parallel\_for}~\cite{intel_tbb}. It generates a logarithmically-deep tree of
tasks, stopping to execute the loop body when the number of iterations is
below the required threshold. Fourth, a programmer may want to execute an active message; that is, to run a
small piece of code on a particular core in the system without waiting for
execution resources to be available. Custom synchronization primitives, for example, execute this way as a function executed on the core where the data
lives. \Grappa provides the \texttt{call\_on} call for this purpose.

@@

>>>>

\Grappa provides four methods for expressing parallelism, shown in
Figure~\ref{fig:expressing-parallelism}. First, when the programmer identifies
work that can be done in parallel, the work may be wrapped up in a function
and queued with its arguments for later execution using a \texttt{spawn}.
Second, a programmer can use \texttt{spawn\_on} to spawn a task on a specific
core in the system or at the home core of a particular memory location. Third,
the programmer can invoke a parallel for loop with \texttt{parallel\_for}, provided that the trip count is
known at loop entry. The programmer specifies a function pointer along with
start and end indices and an optional threshold to control parallel overhead.
\Grappa does {\em recursive decomposition} of iterations, similar to Cilk's
cilk\_for construct~\cite {cilkforimplementation}, and TBB's {\tt
parallel\_for}~\cite{intel_tbb}. It generates a logarithmically-deep tree of
tasks, stopping to execute the loop body when the number of iterations is
below the required threshold. Fourth, a programmer may want to execute an active message; that is, to run a
small piece of code on a particular core in the system without waiting for
execution resources to be available. Custom synchronization primitives, for example, execute this way as a function executed on the core where the data
lives. \Grappa provides the \texttt{call\_on} call for this purpose.

@@

\begin{figure}[htbp]
\begin{scriptsize}
\begin{verbatim}

class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<struct node_t *> *children;
};

void search(GlobalAddress<node_t> node, key_t key) {
  if (node.key == key) {
    result = node;
    return;
  }

  parallel_for(0, node.numChildren, &index) {
    search(node.children[index], key);
  }

}
\end{verbatim}
\end{scriptsize}
\end{figure}
